---
title: "explanation_squared_transformation"
output: html_document
date: "2023-10-26"
---

# Guide: Squared_transformation
This document acts as a guide for the function found in the Squared_Transformation R script also found in this public repository.

**Function**
```{r}
squared_data <- function(data,power) {
  if (power == "square") {
    # Square each element of the vector
    squared_data <- data^2
    return(squared_data)
  } else {
    return("Not available")
  }
}
```

*Explanation*
The function squared_data takes two parameters: data and power. 
It is designed to square the desired data based on the value of power.
It only works if the power desired is "square", otherwise it does not work. 
For example, if you want to cube this data, the function will print "Not available".

- Example
```{r}
data(mtcars) # Load built-in R dataset mtcars 

head(mtcars) # Checks the first few rows of the dataset

squared_cyl <- squared_data(mtcars$cyl,"square") # Apply the function to the 'cyl' column

# Print the result
print(squared_cyl)

squared_cyl <- squared_data(mtcars$cyl,"cube") # Apply the function to the 'cyl' column
# Print the result
print(squared_cyl)
```